raptr: Representative and Adequate Prioritization Toolkit in R

### 2016-11-27 code/rmarkdown/article.Rmd
+ add in document statistics for article + reduce length of abstract, main text and figures to within limits

1. An underlying aim in conservation planning is to maximize the long-term persistence of biodiversity. To fulfill this aim, the ecological and evolutionary processes that sustain biodiversity must be preserved. One way to conserve such processes at the feature level (eg. species, ecosystem) is to preserve a representative sample of the physical attributes that underpin them across the feature's geographic distribution. For example, preserving the adaptive processes currently acting on a species might be crucial for its long-term persistence in a world where environmental change is accelerating. By conserving individuals with the ability to persist in a range of climatic conditions--physical attributes associated with adaptation--protected areas can foster evolutionary processes. Despite this, current approaches overwhelmingly focus on securing a target proportion of each features' geographic range and little attention has been directed towards targeting a representative sample of them.

2. To address this issue, we developed the \\texttt{raptr: Representative and Adequate Prioritization Toolkit in R} to guide reserve selection using targets for representing spatially explicit variables that underpin biodiversity processes as well as more typical area protection targets. Users set \"amount targets\"--similar to conventional reserve selection methods--to secure a target proportion of the features' geographic distributions. Additionally, users set attribute \"space targets\" to ensure that reserve systems also secure a representative sample of ecologically or evolutionary relevant attributes (space) across the features' geographic distributions (eg. an attribute space expressing variation in genetic characteristics between individuals, or variation in climatic conditions between areas). We demonstrate the functionality of this package using simulations and two case studies. We generate solutions that secure a proportion of the species' distributions using amount targets--representing conventional reserve selection--and compare them with solutions generated using both amount and attribute space targets.

3. We show that markedly different solutions emerge when explicitly considering within feature representation in reserve selection. Our simulations suggest that including representativeness in conservation planning is important where biodiversity features have multimodal distributions in an attribute space. The case studies show that explicitly setting space-based targets can result in solutions that preserve a much more representative sample of features. Additionally, the case studies suggest that securing a representative sample of features may not require a much greater area of reservation than traditional approaches.

4. The \\texttt{raptr R} package provides a unified framework for achieving spatial conservation prioritizations that secure an adequate and representative sample of features. Prioritizations that achieve this are likely to result in a greater chance of achieving long-term biodiversity persistence than area-based planning alone.

@@

Short running title: Representative and adequate prioritizations \newline
Abstract word count: XXX / XXX  
Total word count: XXX / XXX  
Number of references: XXX  
Number of figures: XXX  
Number of tables: 0  
Number of textboxes: 0  
Number of equations: XXX

>>>>

1. An underlying aim in conservation is to maximize the long-term persistence of biodiversity. To fulfill this aim, the ecological and evolutionary processes that sustain biodiversity must be preserved. One way to conserve such processes at the feature level (eg. species, ecosystem) is to preserve a representative sample of the physical attributes that underpin them across the feature's geographic distribution. For example, the long-term persistence of a species may depend on its ability to adapt to new climatic conditions. By conserving individuals with the ability to persist in a range of conditions--physical attributes associated with adaptation--protected areas can foster evolutionary processes. Despite this, current reserve selection methods overwhelmingly focus on securing an adequate proportion of features' geographic ranges and little attention has been directed towards capturing a representative sample.

2. To address this issue, we developed the \\texttt{raptr R} package to guide reserve selection using targets for representing spatially explicit variables that underpin biodiversity processes as well as more typical area protection targets. Users set "amount targets"--similar to conventional methods--to secure a target proportion of the features' geographic distributions. Additionally, users set "space targets" to secure a representative sample of variation in ecologically or evolutionary relevant attributes (eg. climatic or genetic variation). We demonstrate the functionality of this package using simulations and two case studies. We generate solutions that secure a proportion of the species' geographic distributions using amount targets--representing conventional methods--and compare them with solutions generated using amount and space targets.

3. We show that different solutions emerge when explicitly considering within feature representation in reserve selection. Our simulations suggest that targeting representativeness is particularly important for biodiversity features that have multimodal distributions in an attribute space. The case studies show that setting space targets can result in solutions that conserve a much more representative sample of features--and this can be achieved with only a slight increase in reserve size.

4. The \\texttt{raptr R} package provides a toolkit for making spatial conservation prioritizations that secure an adequate and representative sample of features. By targeting representativeness, prioritizations may have a greater chance of achieving long-term biodiversity persistence.

@@

Short running title: Representative and adequate prioritizations  
Abstract word count: 350 / 350  
Total word count: 6977 / 7000  
Number of references: 42  
Number of figures: 8  
Number of tables: 0  
Number of textboxes: 0  
Number of equations: 4
